Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-25 submission/Sze_Obesity_PeerJ_2016.Rmd
paragraph1 results edits

***Separate Analysis***
We used the categorical variable of obese or non-obese to analyze each data set separately for significant correlations to Bacteroidetes, Firmicutes, Bacteroidetes/Firmicutes (B/F) ratio, Shannon diversity, OTU richness, evenness, and the Bray-Curtis distance matrix which was a similar approach taken by two previous reviews [@walters_meta-analyses_2014; @finucane_taxonomic_2014]. Using a P-value cutoff for significance as less than 0.05 we found a only 1 significant result for OTU richness. There were no significant results for Bacteroidetes, Firmicutes, or the B/F ratio. The full summary of the exact P-values for each respective study and variable tested can be found in table S1 of the online supplement.

>>>>

***Separate Analysis***
We used the categorical variable of obese or non-obese to analyze each data set separately for significant correlations to Bacteroidetes, Firmicutes, Bacteroidetes/Firmicutes (B/F) ratio, Shannon diversity, OTU richness, evenness, and the Bray-Curtis distance matrix which was a similar approach taken by two previous reviews [@walters_meta-analyses_2014; @finucane_taxonomic_2014]. Using a P-value cutoff for significance as less than 0.05 we found a total of `r length(rownames(alpha_tests.summary[which(alpha_tests.summary$p.value < 0.05 & alpha_tests.summary$metric != "bacteroidetes"), ]))`significant results; two for Shannon diversity, three for observed richness, and one for evenness. There were no significant results for Bacteroidetes, Firmicutes, or the B/F ratio. The full summary of the exact P-values for each respective study and variable tested can be found in table S1 of the online supplement.
